Paper 1

### 2022-05-27 scripts/Paper 1.Rmd
add seasonal rainfall

```{r setup, include=FALSE}
library(dplyr)
library(data.table)
library(janitor)
library(plotly)
library(plyr)
library(knitr)
library(tidyverse)
#library(devtools)
library(openair)
library(tidyr)
library(naniar)

@@

rainfall_L %>% mutate(Precip = replace_na(Precip, 0)) %>%
  ddply(c("Year", "Month"), summarise,
  monthly.total = sum(Precip)) %>%
  ggplot(., aes(x = Month, y = monthly.total, group = Year, fill = Year)) +
       scale_x_discrete(limits = month.abb) +
  geom_col(position = "dodge") + 
  ylab("Monthly rainfall (mm)")+
  xlab("Month")+
  theme_classic()

@@

```{r Air temperature, echo=FALSE, message = FALSE, fig.width = 10, fig.height = 4}

ggplotly(ggplot(input.daily, aes(x = jday, y = Ta.mean, group = Year)) +
  geom_line(aes(color = Year))+
     geom_ribbon(aes(ymin=Ta.min, ymax=Ta.max), alpha=.3, linetype=0) +
  theme_classic())

@@

```{r timeseries analysis}
library(forecast)

@@

>>>>

```{r setup, include=FALSE}
library(dplyr)
library(data.table)
library(janitor)
library(plotly)
library(plyr)
library(knitr)
library(tidyverse)
#library(devtools)
library(openair)
library(tidyr)
library(naniar)
library(forecast)

@@

rainfall_L %>% mutate(Precip = replace_na(Precip, 0)) %>%
  ddply(c("Year", "month"), summarise,
  monthly.total = sum(Precip)) %>%
  ggplot(., aes(x = month, y = monthly.total, group = Year, fill = Year)) +
       scale_x_discrete(limits = month.abb) +
  geom_col(position = "dodge") + 
  ylab("Monthly rainfall (mm)")+
  xlab("month")+
  theme_classic()

@@

```{r Air temperature, echo=FALSE, message = FALSE, fig.width = 10, fig.height = 4}
ggplotly(ggplot(input.daily, aes(x = jday, y = Ta.mean, group = Year)) +
  geom_line(aes(color = Year))+
     geom_ribbon(aes(ymin=Ta.min, ymax=Ta.max), alpha=.3, linetype=0) +
  theme_classic())

@@

```{r add seasons, include=FALSE}
rainfall$season <- "" # add season variable

# define seasons
winter <- (rainfall$month == "6" | rainfall$month == "7" | rainfall$month == "8")
spring <- (rainfall$month == "9" | rainfall$month == "10" | rainfall$month == "11")
summer <- (rainfall$month == "12" | rainfall$month == "1" | rainfall$month == "2")
autumn <- (rainfall$month == "3" | rainfall$month == "4" | rainfall$month == "5")

rainfall$season[winter] <- "Winter"
rainfall$season[spring] <- "Spring"
rainfall$season[summer] <- "Summer"
rainfall$season[autumn] <- "Autumn"

season_levelorder <-  c('Summer', 'Autumn', 'Winter', 'Spring')

rainfall$season <- factor(rainfall$season , levels=c('Summer', 'Autumn', 'Winter', 'Spring'))
```

```{r create rainfall summary}
rainfall.summary <- rainfall %>% ddply(c("Year", "Site", "season"), summarise,
                                       seasonal.sum = sum(Precip, na.rm = TRUE))
rainfall.summary %>% 
  ggplot(., aes(x = season, y = seasonal.sum, group = Year, fill = Site)) +
  geom_col(position = "dodge", aes(fill = Year)) + 
  ylab("Monthly rainfall (mm)")+
  xlab("month")+
  theme_classic()

@@

```{r timeseries analysis}
library(forecast)
```
